Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-03-19 paper.tex
Move exp C_P curves into numerical setup section

\section{Turbine description}

In this study we seek to predict the near-wake of the UNH-RVAT turbine, shown in
Figure~\ref{fig:RVAT-CAD}. Experimental performance curves for the UNH-RVAT are
shown in Figure~\ref{fig:exp_perf}. We modeled the turbine at a tip speed ratio
$\lambda=1.9$, which corresponds to the maximum power coefficient, and a turbine
diameter Reynolds number $Re_D \approx 10^6$, which corresponds to a
$Re$-independent state for both performance and near-wake characteristics, as
determined from experimental measurements \cite{Bachant2014,
    Bachant2016-RVAT-Re-dep}.

\begin{figure}[ht]
    \centering

    \includegraphics[clip, trim=0 1in 0 1in, width=0.8\textwidth]{figures/CAD}

    \label{fig:RVAT-CAD}
\end{figure}

\begin{figure}[ht]
    \centering

@@

    \label{fig:exp_perf}
\end{figure}

In this study the UNH-RVAT baseline tow tank experiment was simulated using a
mean rotor tip speed ratio $\lambda=1.9$, which corresponds to the maximum
measured power coefficient. The tow speed or free stream velocity $U_\infty=1.0$
m/s gives a turbine diameter Reynolds number $Re_D \approx 10^6$, which
corresponds to the $Re$-independent state for both performance and near-wake
characteristics, as determined from previous experimental measurements
\cite{Bachant2014, Bachant2016-Energies}.

>>>>

In this study the UNH-RVAT baseline tow tank experiment was simulated using a
mean rotor tip speed ratio $\lambda=1.9$, which corresponds to the maximum
measured power coefficient; cf. Figure~\ref{fig:exp-perf}. The tow speed or free
stream velocity $U_\infty=1.0$ m/s gives a turbine diameter Reynolds number
$Re_D \approx 10^6$, which corresponds to the $Re$-independent state for both
performance and near-wake characteristics, as determined from previous
experimental measurements \cite{Bachant2014, Bachant2016-Energies}.

@@

    \label{fig:exp-perf}
\end{figure}
